---
title: "Phone_Forecast"
author: "Andrew Carlston"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: none
    df_print: paged
    highlight: tango
    theme: flatly
    toc: yes
    toc_depth: 1
params:
  cx: 1.15
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
    out.width = "100%",
    out.height = "500px",
    fig.pos = "center",
    dpi = 300)
```

```{r libraries}
library(tidyverse)
library(lubridate)
library(tidyquant)
library(plotly)
library(shiny)
library(openxlsx)
library(DT)
```

# Customer Count

Customer Count is being used as predictive variable that controls the growth rate of the forecast. This Value is being produced by the product team.

-   Updated column is using the percentage 2024 growth rate by month while:
    -   subtracting the added growth rate from product team \~ 11 %
    -   adding `r sprintf("%.0f%%", (params$cx - 1) * 100)` growth from 2022 as requested
-   The 2024 values are including the the growth rate product supplied

```{r data}
sys.source("../00_Scripts/functions.R", envir = env <- new.env())

cx <- env[["customer_count_data"]]() 
cx_up <- env[["cx_up"]](cx,value = params$cx)
cx_chart_up <- env[["cx_chart_up"]](cx,value = params$cx)

```

<details>

<summary>Click to show/hide data table and chart</summary>

<p>

##  {.tabset .tabset-fade .tabset-pills .no-tabset-title}

### Table

```{r table}
cx_tbl <- cx_up %>%  
  DT::datatable(
    extensions = c('Buttons', 'Scroller'),
    options = list(
      dom = 'Blrtip',
      buttons = list(
        list(
          extend = 'excel',
          text = 'Export to Excel'
        ),
        list(
          extend = 'csv',
          text = 'Export to CSV'
        )
      ),
      defaultPageSize = 50,
      scrollY = "450px",
      scrollX = TRUE,
      scroller = TRUE,
      rowStyle = "function(index, row, dt) { if (index % 2 === 1) { return { classes: 'even' }; } }",
      style = "font-size: 12px;"
    )
  )
cx_tbl
```

### Chart

```{r chart}
chart_up <- cx_chart_up %>% 
  ggplot(aes(x = Month, y = Customer_Count, color = as.factor(Group), group = as.factor(Group), linetype = as.factor(Group))) +
  geom_line() +
  labs(x = "Month", y = "Customer Count", color = "Group") +
  scale_color_manual(values = c("orange", "blue", "green", "red")) +
  scale_linetype_manual(values = c("solid", "solid", "solid", "dotted")) +
  theme_minimal()

plotly::ggplotly(chart_up)
```

</p>

</details>
