---
title: "Phone_Forecast"
author: "Andrew Carlston"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: none
    df_print: paged
    highlight: tango
    theme: flatly
    toc: yes
    toc_depth: 1
params:
  cx: 1.3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
    out.width = "100%",
    out.height = "500px",
    fig.pos = "center",
    dpi = 300)
```

```{r libraries}
library(DT)
library(tidyverse)
library(lubridate)
library(tidyquant)
library(plotly)
library(shiny)
library(openxlsx)
library(ggrepel)


```

# Customer Count

Customer Count is being used as predictive variable that controls the growth rate of the forecast. This Value is being produced by the product team.

-   Updated column is using the percentage 2024 growth rate by month while:
    -   subtracting the added growth rate from product team \~ 11 %
    -   adding `r sprintf("%.0f%%", (params$cx - 1) * 100)` growth from 2022 as requested
-   The 2024 values are including the the growth rate product supplied

```{r data}
sys.source("../00_Scripts/functions.R", envir = env <- new.env())

# Customer count Data
cx_data <- env[["customer_count_data"]]() 


# Provider Data
Provider_Forecast <- read_csv("../00_Data/Provider_Forecasts/Phone/h20_Provider_Phone_2023-07-17_12_37_.csv")




```

<details>
<summary>Customer Data</summary>
## {.tabset .tabset-fade .tabset-pills .no-tabset-title}

### Table

```{r table cx}
cx_up %>%  
  DT::datatable(
    extensions = c('Buttons', 'Scroller'),
    options = list(
      dom = 'Blrtip',
      buttons = list(
        list(
          extend = 'excel',
          text = 'Export to Excel'
        ),
        list(
          extend = 'csv',
          text = 'Export to CSV'
        )
      ),
      defaultPageSize = 50,
      scrollY = "450px",
      scrollX = TRUE,
      scroller = TRUE,
      rowStyle = "function(index, row, dt) { if (index % 2 === 1) { return { classes: 'even' }; } }",
      style = "font-size: 12px;"
    )
  )
```

### Chart

```{r chart cx}
chart_up <- cx_chart_up %>% 
  ggplot(aes(x = Month, y = Customer_Count, color = as.factor(Group), group = as.factor(Group), linetype = as.factor(Group))) +
  geom_line() +
  labs(x = "Month", y = "Customer Count", color = "Group") +
  scale_color_manual(values = c("orange", "blue", "green", "red")) +
  scale_linetype_manual(values = c("solid", "solid", "solid", "dotted")) +
  theme_minimal()

plotly::ggplotly(chart_up)
```


# Forecast
</details>
<details>
<summary>Forecast Data</summary>
## {.tabset .tabset-fade .tabset-pills .no-tabset-title}

### Table

```{r table provider}
Provider_Phone %>%  
  DT::datatable(
    extensions = c('Buttons', 'Scroller'),
    options = list(
      dom = 'Blrtip',
      buttons = list(
        list(
          extend = 'excel',
          text = 'Export to Excel'
        ),
        list(
          extend = 'csv',
          text = 'Export to CSV'
        )
      ),
      defaultPageSize = 20,
      scrollY = "450px",
      scrollX = TRUE,
      scroller = TRUE,
      rowStyle = "function(index, row, dt) { if (index % 2 === 1) { return { classes: 'even' }; } }",
      style = "font-size: 12px;"
    )
  )
```

### Chart

```{r chart provider}

modified_df <- Provider_Phone

# Get unique values of holiday_name_event for assigning shapes
unique_holidays <- unique(modified_df$holiday_name_event)


forecast_Chart <- ggplot(modified_df, aes(x = Date, y = Forecast, group = .key, color = .key)) +
  geom_line() +
  geom_text_repel(aes(label = holiday_name_event), hjust = 0, vjust = 1, nudge_x = 0.1, size = 3) +
  geom_point(data = modified_df[!is.na(modified_df$holiday_name_event), ], aes(shape = holiday_name_event), size = 4) +
  scale_shape_manual(values = 1:length(unique_holidays)) +
  labs(title = "Forecast by Group",
       x = "Date",
       y = "Forecast",
       color = "Group") +
  theme_minimal() +
  coord_cartesian(ylim = c(0, NA))

plotly::ggplotly(forecast_Chart)
```
</details>
